Constant-round Blind Classical Verification of Quantum Sampling

### 2020-04-14 qpip0.tex
Updates from Overleaf

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the prover will produce a $z$ \Ethan{Prover will produce isn't right, the one producing z should be verifier} on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}

>>>>

\begin{lemma}\label{lem:urmila-binding}[binding property of  Protocol~\ref{proto:urmila4}\cite{FOCS:Mahadev18a}]
If a prover's strategy in Protocol~\ref{proto:urmila4}\hannote{need clarification} results in passing the testing round with probability $1-\negl(n)$, then there must exist a $\rho$ such that for all $h$, the verifier will produce a $z$ on the Hadamard round that is $\negl(n)$-Q-computationally indistinguishable\footnote{Recall that quantum computational indistinguishability is defined in Definition~\ref{def:comp-indis}.} from $M_{XZ}(\rho,h)$\hannote{add notation}, unless LWE can be efficiently solved by a quantum computer. 
\end{lemma}
